Information Transfer in Multi-Task Learning via a Bias-Variance Decomposition in High Dimensions

### 2020-08-10 arxiv/experiments.tex
restructure

\vspace{-0.07in}
\subsection{Experimental Setup}

@@

%\textbf{The training procedure and baseline.}
For all models, we use a shared module for all tasks and assign a separate output layer on top of the shared module for each task.
The baseline training schedule for MTL is the round-robin training schedule.
%We compare our incremental training schedule of Algorithm \ref{alg_inc_train} to the round-robin training schedule.
We measure the test accuracy of predicting a target task.
We measure computional cost by summing over all epochs the number of samples used in every epoch.

\vspace{-0.07in}
\subsection{Experimental Results}\label{sec_exp_res}

@@

\vspace{-0.07in}
\subsection{Validating the Theoretical Results}\label{sec_exp_ab}

>>>>

\subsection{Experimental Setup}

@@

%\textbf{The training procedure and baseline.}
For all models, we use a shared module for all tasks and assign a separate output layer on top of the shared module for each task.
The baseline training schedule for MTL is the round-robin training schedule.
%We compare our incremental training schedule of Algorithm \ref{alg_inc_train} to the round-robin training schedule.
We measure the test accuracy of predicting a target task.
We measure computational cost by summing over all epochs the number of samples used in every epoch.

\subsection{Simulation Studies}

\subsection{Validating the Theoretical Implication}\label{sec_exp_ab}

\subsection{Validating the Algorithmic Consequences}\label{sec_exp_res}

@@
